BlogForever Crawler: Techniques and Algorithms\\to Harvest Modern Weblogs

### 2013-12-03 tex/3-algorithms.tex
3.3 fixed.

This section explains in detail the algorithms we developed to extract blog posts' content and its variations for authors, dates and comments.
We explain how we take advantage of blog specific characteristics to build extraction rules applicable to all posts of a blog.
Our focus is on minimising the algorithmic complexity while keeping our approach simple and generic.

@@

\TODO{Assumption is not a good word, we are based on facts from previous work.}
% I suggest that you restructure this part as follows:

% Having blogs as our target websites, we are taking into account the following facts that play a central role in the extraction process.

% 1. "Blog is a kind of web page [with] frequent, usually brief posts, with the immediacy of reverse chronological order" (+ ref to BlogForever D2.2: BlogForever Data Model
% https://zenodo.org/record/7488/files/BlogForever\_D2\_2WeblogDataModel.pdf

% 2. blogs provide web feeds: structured and standardised views of the most recent blog posts.

% 3. Web feeds contain information regarding the latest blog posts (usually 10 or 20 entries) + ref

% 4. posts of the same blog share a similar HTML structure.

% Consequently, in order to effectively archive old blog content, it is necessary to download and process pages beyond the ones referenced in web feeds.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Extraction rules and string similarity}
\label{extractionrulesandstringsimilarity}

@@

% string similarity
Unsurprisingly, the choice of the string similarity algorithm greatly influences the running time and precision of the extraction process. We chose the Sørensen–Dice coefficient similarity\cite{dice1945}, which, to the best of our knowledge, is the only string similarity algorithm fulfilling the following criteria:

@@

Properties \ref{wordorderProp} and \ref{lengthProp} are essential to deal with cases where a blog's web feed only contains an abstract or a subset of the entire post content. Table \ref{similarityTable} gives examples to illustrate how these two properties are fulfilled by the Sørensen–Dice coefficient similarity but do not hold for \emph{edit distance} based similarities such as the Levenshtein\cite{levenshtein1966} similarity.

@@

\TODO{similatiry -> score function}
\similarityAlgo

>>>>

This section explains in detail the algorithms we developed to extract blog posts' article and its variations for authors, dates and comments.
We explain how we take advantage of blog specific characteristics to build extraction rules applicable to all posts of a blog.
Our focus is on minimising the algorithmic complexity while keeping our approach simple and generic.

@@

\TODO{Assumption is not a good word, we are based on facts from previous work.}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\clearpage
\subsection{Extraction rules and string similarity}
\label{extractionrulesandstringsimilarity}

@@

% score function := string similarity
Unsurprisingly, the choice of \code{ScoreFunction} greatly influences the running time and precision of the extraction process. When targeting articles, extraction rules are scored with a string similarity function comparing extracted and target strings. We chose the Sørensen–Dice coefficient similarity\cite{dice1945}, which, to the best of our knowledge, is the only string similarity algorithm fulfilling the following criteria:

@@

Properties \ref{wordorderProp} and \ref{lengthProp} are essential to deal with cases where a blog's web feed only contains an abstract or a subset of the entire post article. Table \ref{similarityTable} gives examples to illustrate how these two properties are fulfilled by the Sørensen–Dice coefficient similarity but do not hold for \emph{edit distance} based similarities such as the Levenshtein\cite{levenshtein1966} similarity.

@@

\similarityAlgo

### 2013-12-03 tex/4-techniques.tex
3.3 fixed.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Enriching Scrapy}\label{enrichingscrapy}
% Into, blog post identification
In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog post identification} and \emph{download priority heuristic}. Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last-in-first-out} manner. The \emph{blog post identification} function is able to identify from an URL whether or not the corresponding page is a blog post. Internally, this function uses a regular expression constructed for each blog from it's web feed entries. These constitute the only set of known blog post URLs, and can therefore be used to identify the structure of blog post URLs. This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non-post pages (or false positive will occur). In practice this assumption held for all blog platforms we encountered during the developments and seems to be a common practice among web developer.

@@

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Enriching Scrapy}\label{enrichingscrapy}
% into
In order to identify web pages as blog posts, our implementation enriches Scrapy with two components to narrow the extraction process to the subsets of blog pages holding blog posts: \emph{blog post identification} and \emph{download priority heuristic}.

% blog post identification
Given an entry point to a website, the default Scrapy behavior allows to look over all pages of the same domain in a \emph{last-in-first-out} manner. The \emph{blog post identification} function is able to identify from an URL whether or not the corresponding page is a blog post. Internally, this function uses a per blog regular expression constructed from web feed entry URLs. This simple approach requires that blogs use the same pattern for all posts (or false negative will occur) which has to be distinct for non-post pages (or false positive will occur). In practice this assumption held for all blog platforms we encountered during the developments and seems to be a common practice among web developer.

@@

\TODO{Give more details: this function implements a string score predictor using a the Distance-Weighted k-Nearest-Neighbor classifier, as described in \cite{dudani1976} http://ieeexplore.ieee.org/xpls/abs\_all.jsp?arnumber=5408784 This predictor can be used as an active machine learning algorithm by feeding it little by little with new url/score as they are discovered.}
